Blum axioms and nondeterministic computation of functions

### 2016-04-08 paper.tex
paper.tex: Demote the section about  Blum axioms to a subsection and change its beginning.

\section{Blum axioms}
\label{sec:blum-axioms}

With the mathematical notion of an acceptable Gödel numbering,
we can now define the Blum axioms for complexity measures.

>>>>

\subsection{Efficiency criterion: Blum axioms}
\label{sec:blum-axioms}

The \emph{complexity} of a computation is how much of a resource
that is invested in that computation~\cite[p.~285]{HopcroftUllman1979}.
For each model of computation and each resource under that model,
we can establish a \emph{complexity measure} concerning that resource.
This section is devoted to formalizing this notion.

Note that the complexity measure must be subordinated to the machine model.
For instance,
if we are talking about pushdown automata with two stacks,
we could restrict the machine to operate on one stack each time
(that is, each move must alter at most one stack)
and measure the number of times the automaton switches its ``active'' stack.
This complexity measure makes no sense for Turing machines,
which have no stacks.

Therefore,
we must have an acceptable Gödel numbering $\phi$
to discuss complexity.
We can think that a complexity measure is a way of associating
each program $w$ and each input $x$
with a number $n$,
which is the amount of the measured resource it takes to obtain $\phi_w(x)$
using the program $w$.

As we did with the machine encodings,
we will impose some restrictions on what can be a complexity measure
to be able to manipulate it (at least indirectly).
In our case,
we will use Blum axioms~\cite[p.~324]{Blum1967}.
